Search-based Synthesis of Network Intrusion Detection Rules

### 2019-10-04 paper/paper.tex
fix pass on table 1
pass on table I

\begin{table*}[t!]
  \caption{\label{table:attacks}Characterization of attacks analyzed
    and Golden Rule of Suricata (reference) to capture it.\Mar{please,
  show me the Golden Rule, \ie{} the part that is relevant of each rule (for
  capturing the negative traffic precisely)}}  
  \centering
  \begin{tabular}{lllll}
    \toprule
    \multicolumn{1}{c}{Name} & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{Protocol} & \multicolumn{1}{c}{Description} & \multicolumn{1}{c}{Golden Rule} \\
    \midrule
    GET/POST Flood & multiple & HTTP & Denial of Service & - \\      
    Ping Scan & single & ICMP & Discovers active hosts in a network &  - \\
    Black Nurse & multiple & ICMP & Denial of Service & - \\
    Ping Flood  & multiple & ICMP & Denial of Service & - \\  
    Port Scan TCP & single & TCP & Discovers open ports in a host & -  \\
    SYN Flood & multiple & TCP & Denial of Service & - \\
    Port Scan UDP & single & UDP & Discovers open ports in a host & - \\        
    \bottomrule
  \end{tabular}
\end{table*}

>>>>

\begin{table*}[t!]
  \caption{\label{table:attacks}Characterization of attacks analyzed
    and Golden Rule of Suricata (reference) to capture it.\Mar{please,
  show me the Golden Rule, \ie{} the part that is relevant of each rule (for
  capturing the negative traffic precisely)}}  
  \centering
  \begin{tabular}{lllll}
    \toprule
    \multicolumn{1}{c}{Name} & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{Protocol} & \multicolumn{1}{c}{Description} & \multicolumn{1}{c}{Golden Rule} \\
    \midrule     
    Ping Scan & single & ICMP & Discovers active hosts in a network &  dsize:0; itype:8; \\
    Black Nurse & multiple & ICMP & Denial of Service & itype:3; icode:3; detection\_filter:track by\_dst, count 250, seconds 1;\\
    Ping Flood  & multiple & ICMP & Denial of Service & itype:8; icode:0; detection\_filter:track by\_src, count 30, seconds 1;\\  
    Port Scan TCP & single & TCP & Discovers open ports in a host & flags: A; ack: 0;dsize: 0; \\
    SYN Flood & multiple & TCP & Denial of Service & flags: S,12; threshold: type both, track by\_dst, count 5000, seconds 5;\\
    UDP Flood & multiple & UDP & Denial of Service & fragbits:M; threshold: type both, track by_dst, count 5000, seconds 5; \\
    \bottomrule
  \end{tabular}
\end{table*}
